### 2022-11-21 manuscript.Rmd

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
    - R/run_simulation.R
  files:
    - intermediate_results_separability.zip
    - intermediate_results_reliability.zip
    - intermediate_results_type1error_1.zip
    - intermediate_results_type1error_2.zip
    - intermediate_results_type1error_3.zip
---

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
  files:
    - intermediate_results.zip
---
